---
title: “Comparing Model Accuracy at Different Horizons”
author: “David Holt”
date: “3/19/2020”
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forecast)
library(fable)
library(tsibble)
library(tsibbledata)
library(tsbox)
```
## Time series of interest
First and foremost, I love the `tsibble` package. It’s the most sensible thing to happen to time series analysis in R since, well, `forecast`.
Additionally, I love `tsbox` for making my <insert time series format> into a tsibbles.
```{r data}
wine <- forecast::wineind %>%
    tsbox::ts_tsibble() %>%
    tsibble::index_by(month = tsibble::yearmonth(time)) %>%
    tsibble::update_tsibble(index = month) %>%
    dplyr::select(-time)
```
## Examine time series
I love `feasts`, for all the time series-specific plotting.
```{r plots1}
feasts::autoplot(wine, value)
```
## Model time series
I also love `fable`, for bringing forecasting into the world of tidy data. Look at all the models!
```{r model}
models <-
    wine %>%
    fabletools::model(
        mean = fable::MEAN(value)
        ,rw_drift = fable::RW(value ~ drift())
        ,naive = fable::NAIVE(value)
        ,snaive = fable::SNAIVE(value)
        ,ets = fable::ETS(value)
        ,arima = fable::ARIMA(value)
    )
models
```
## Forecast time series
`fable` makes it just as easy to forecast all those models, too. Let’s forecast 6 months!
```{r forecast}
forecasts <- fabletools::forecast(models, h = 6)
forecasts
```
## Plot forecasts
It just keeps getting better...
```{r plot_forecasts}
feasts::autoplot(forecasts, wine) +
    ggplot2::lims(x = c(as.Date(“1993-01-01"), NA)) +
    ggplot2::facet_wrap(~ .model, ncol = 2)
```
## Test model fit
Getting fit statistics from the models is a breeze.
```{r fit}
accuracy <- fabletools::accuracy(models)
```
## Test model performance on a holdout
Of course, we don’t just want to look at fit. We like rigor. We demand a holdout.
... still easy! And it’ll show you how simple the whole thing is when piped.
```{r holdout}
wine %>%
    filter(lubridate::year(month) < 1994) %>%
        fabletools::model(
        mean = fable::MEAN(value)
        ,rw_drift = fable::RW(value ~ drift())
        ,naive = fable::NAIVE(value)
        ,snaive = fable::SNAIVE(value)
        ,ets = fable::ETS(value)
        ,arima = fable::ARIMA(value)
    ) %>%
    fabletools::forecast(h = 6) %>%
    feasts::autoplot(wine) +
    ggplot2::lims(x = c(as.Date(“1993-01-01”), NA)) +
    ggplot2::facet_wrap(~ .model, ncol = 2)
```
